Interference Transform: Estimating the frequency and phase of low resolution samples

### 2020-05-18 Papers/01_interf_transf/Interference Transform.tex
adjusting typesseting tools
added ghostscript to compress pdf

\documentclass{article}

\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}

@@

\subsection{Theory}

>>>>

\documentclass{article}
\usepackage{amsfonts} % \mathbb
\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

@@

\subsection{Theory}
  One can represent the discrete wave as an an array $ W[i] $ of $ n-1 $ real numbers. Such wave is related, as illustrated in figure \ref{fig:ContinuousVsDiscrete}, to an hypothetical continuous wave $ S(t) $ of which its components are sampled in uniform time intervals at a rate of $\textrm{fps}$ frames per second.

  \begin{figure}[h!]
    \centering
      \includegraphics[width=0.8\linewidth]{images/01ContinuousVsDiscrete}
    \caption{Discrete samples (black points) from a continuous wave (grey line). Note that the amplitude is also truncated}
    \label{fig:ContinuousVsDiscrete}
  \end{figure}

  Thus, we have:
  $ W[i] \in \mathbb{R} \forall i \in \mathbb{N}, 0 \le i < n $,
  $ S(t) \in \mathbb{R} \forall t \in \mathbb{R}, 0 \le t < t_f $ where $ t_f=n / \textrm{fps} $
